Loop

### 2021-04-07 executableMS/ms_v1.rmd
Update ms_v1.rmd

# pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
```
Loading data & functions
```{r}
data <- readRDS(data_clean.rds) 
procedures <- read_csv(github://itchyshin/mice_sex_diff/export/procedures.csv)
n <- length(unique(data$id))

@@

  group <- read_csv(here("data", "ParameterGrouping.csv"))

>>>>

# pacman::p_load(readr, dplyr,metafor, devtools, purrr, tidyverse, tidyr, tibble, kableExtra, robumeta, ggpubr, ggplot2, png, grid, here, knitr, pander, splus2R)
```
Loading data & functions
```{r}
data <- readRDS(github://itchyshin/mice_sex_diff/export/data_clean.rds) 
procedures <- read_csv(github://itchyshin/mice_sex_diff/data/procedures.csv)
n <- length(unique(data$id))

@@

  group <- read_csv((github://itchyshin/mice_sex_diff/data/ParameterGrouping.csv)
